QDNAseq segmentation

### 2019-10-16 QDNAseq segmentation.Rmd
...

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

@@

val.info = do.call(bind_rows, lapply(sheets, function(s) {
  readxl::read_xlsx(val.file, s) %>% dplyr::select(`Hospital Research ID`, matches('Status'), `Block ID`,`Sample Type`, `SLX-ID`, `Index Sequence`, Cohort, Batch, RA, matches('Collection')) %>% 
    dplyr::filter(!is.na(`SLX-ID`)) %>% mutate_at(vars(`SLX-ID`, `Block ID`), list(as.character)) 
})) %>% mutate(Samplename = paste(`SLX-ID`,`Index Sequence`, sep='.')) %>% 
  rowwise %>% mutate_at(vars(`SLX-ID`), list(pastefun) ) %>% ungroup %>% 
  mutate(
  `Hospital Research ID` = str_replace_all( str_remove_all(`Hospital Research ID`, " "), '/', '_'), 
  `Index Sequence` = str_replace_all(`Index Sequence`, 'tp', ''),
  Samplename = paste(`SLX-ID`,`Index Sequence`,sep='.')
  )

@@

per.sample.var = do.call(bind_rows, lapply(list.files(analysis.dir, 'variance.tsv', recursive=T, full.names=T), function(f) {
  read_tsv(f, col_types='cddd') %>% mutate(patient = basename(sub('plots','',dirname(f))))
})

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(kableExtra)

@@

val.info = do.call(bind_rows, lapply(sheets, function(s) {
  readxl::read_xlsx(val.file, s) %>% dplyr::select(`Hospital Research ID`, matches('Status'), `Block ID`,`Sample Type`, `SLX-ID`, `Index Sequence`, Pathology, Cohort, Batch, matches('Collection|Notes')) %>% 
    dplyr::filter(!is.na(`SLX-ID`)) %>% mutate_at(vars(`SLX-ID`, `Block ID`), list(as.character)) 
})) %>% mutate(Samplename = paste(`SLX-ID`,`Index Sequence`, sep='.')) %>% 
  rowwise %>% mutate_at(vars(`SLX-ID`), list(pastefun) ) %>% ungroup %>% 
  mutate(
  `Hospital Research ID` = str_replace_all( str_remove_all(`Hospital Research ID`, " "), '/', '_'), 
  `Index Sequence` = str_replace_all(`Index Sequence`, 'tp', ''),
  Samplename = paste(`SLX-ID`,`Index Sequence`,sep='.')
  )

@@

per.sample.var = do.call(bind_rows, lapply(list.files(analysis.dir, 'variance.tsv', recursive=T, full.names=T), function(f) {
  read_tsv(f, col_types='cddd') %>% mutate(patient = basename(sub('plots','',dirname(f))))
})) %>% dplyr::select(patient, Samples, everything())

max.bin<-function(bin15,bin50,bin100) {
  if (!is.na(bin100))
    return(100)
  if (!is.na(bin50))
    return(50)
  return(15)
}

per.sample.bin = per.sample.var %>% group_by(Samples) %>% dplyr::summarise( max.bin = max.bin(`15kb`,`50kb`,`100kb`) ) %>% arrange(max.bin)

per.sample.bin %>% group_by(max.bin) %>% tally() %>% spread(max.bin,n) %>% kable(caption = 'Number of samples per QDNAseq bin size') %>% kable_styling('striped', full_width = F)
```

```{r}

per.sample.bin = val.info %>% dplyr::select(matches('Hospital|Status|Block|Pathology|Samplename')) %>% 
  left_join(per.sample.bin, by=c('Samplename'='Samples'))

per.sample.bin %>% group_by(max.bin, Status) %>% tally()

per.sample.bin %>% filter(is.na(max.bin))
